---
title: "Narrative.rmd"
author: "Bryce Farabaugh"
date: "12/10/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Summary:
For this project, I found outdated datasets detailing nuclear weapon information (both arsenal size and nuclear weapons tests) and updated the datasets by adding post-2014 information. I then merged the nuclear weapon datasets into the Correlates of War National Material Capabilities (NMC) dataset which includes information on such variables as military expenditures, military personnel, etc to calculate a “Composite Index of National Capability (CINC)”, a score meant to reflect a state’s military power but which doesn’t account for nuclear weapons (likely the most powerful military deterrent in history.) I updated the data using a tool we didn’t cover in class, “add_row” from the Tibble package
	After updating and merging the datasets, I then made two plots: a line plot showing nuclear arsenals since 1945 as well as a bar plot showing which states possess the most nuclear weapons in 2020. I originally intended to somehow plot CINC as a function of the number of nuclear weapons possessed by nuclear weapon states and draw some conclusions from the resulting information but I don’t yet have the statistical training required to make such an analysis. Nevertheless, I think integrating nuclear weapon information in the Correlates of War database is an interesting and useful contribution and I intend to use the data for further research moving forward. 

Challenges:
The main challenges for this project were locating the original datasets, finding supplemental information to update the datasets, editing the datasets, merging the datasets, and plotting the relevant information. S

Solutions: In terms of locating the original dataset, I found a page on "Our World in Data" that hosted several datasets with outdated information on nuclear weapons pre-2014. I supplemented this data with the latest information from Hans Kristensen's "Nuclear Notebook" series, but as the Nuclear Notebook isn't published every year, some information is "NA."
Editing the datasets was a somewhat arduous task within R that entailed using "add_row" for each missing observation. 
Merging the datasets required ensuring variables were the same across all dataframes and using left_join to combine.
Plotting the information required first deciding what information I wanted to focus on and then editing the code to get the desired aesthetics.

Results: the results are a "merged" dataframe and CSV that includes all information from the original NMC dataset as well as information about nuclear arsenals and tests, as well as two plots (a line plot and bar plot.)

Citations:
The original datasets were pulled from "Our World in Data- Nuclear Weapons", found at https://ourworldindata.org/nuclear-weapons

The National Material Capabilities dataset can be found on the Correlates of War website at https://correlatesofwar.org/data-sets

The current Nuclear Notebook can be found at https://fas.org/issues/nuclear-weapons/status-world-nuclear-forces/ and past versions can be found at http://explore.tandfonline.com/page/pgas/rbul-nuclear-notebooks/

```{r}
knitr::include_graphics(path = "Screenshot (109).png")
```

```{r}
knitr::include_graphics(path = "Screenshot (106).png")
```

```{r}
knitr::include_graphics(path = "Screenshot (107).png")
```




